Statically Typed String Sanitation Inside a Python (Technical Report)

### 2014-12-16 sanitation-psp14/tr/strings_chapter.tex
finished preservation.

The only applicable typing rule is P-T-Concat, so $\emptyset \vdash \iota_1 : \str$
and $\emptyset \vdash \iota_2 : \str$ where $\tau = \str$. 
By induction, $\emptyset \vdash \iota_1' : \str$,
so $\emptyset \vdash \rconcat{\iota_1'}{\iota_2} : \str$.

@@

The only applicable typing rule is P-T-Concat, so $\emptyset \vdash \iota_1 : \str$
and $\emptyset \vdash \iota_2 : \str$ where $\tau = \str$. 
By induction, $\emptyset \vdash \iota_1' : \str$,
so $\emptyset \vdash \rconcat{\iota_1}{\iota_2'} : \str$.

\todo{Everything above in the $\lambdap$ section was sleep deprived plane work -- need to check}

>>>>

The only applicable typing rule is P-T-Concat, so $\emptyset \vdash \iota_1 : \str$
and $\emptyset \vdash \iota_2 : \str$. 
By induction, $\emptyset \vdash \iota_1' : \str$,
so $\emptyset \vdash \rconcat{\iota_1'}{\iota_2} : \str$.

@@

The only applicable typing rule is P-T-Concat, so $\emptyset \vdash \iota_1 : \str$
and $\emptyset \vdash \iota_2 : \str$. 
By induction, $\emptyset \vdash \iota_1' : \str$,
so $\emptyset \vdash \rconcat{\iota_1}{\iota_2'} : \str$.
